---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# thelist

<!-- badges: start -->
<!-- badges: end -->

The goal of thelist is to read data from the Tasmania TheLIST service, for local authority data layers. 

## Installation

You can install thelist from github with

``` r
remotes::install_github("mdsumner/thelist")
```

## Example

This is a basic example which shows how to find the matching cadastral parcel for a given address in the state of Tasmania, without downloading the data layers or reading every data element. 

```{r example}
library(thelist)
library(lazysf)

address <- lazysf(thelist_wfs(), thelist_layer("address"))
library(dplyr)
pid <- address %>% dplyr::filter(ST_NO_FROM == 177, STREET == "LIVERPOOL") %>%
  select(ST_NO_FROM, STREET, PID) %>% collect()
```

See that there are many layers to choose from. 

```{r layers}
writeLines(list_layers)
```

And we can find one of these, by pattern or at random. 

```{r chooselayer}
(lga_layer <- thelist_layer("government_areas"))
thelist_layer(random = TRUE)
```

We can just read direct with sf. 

```{r}
library(sf)
lga <- read_sf(thelist_wfs(), lga_layer)

```
